---
title: "Machine Learning to predict EUR in Permian"
author: "Dario H. Romero, MSc - CPQ Energy & Analytics <http://www.cpq-energy.com>"
date: "August 30, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a document that outlines a workflow to predict EUR (Estimated Ultimate Recovery) by using a  
Supervised Learning algorithm in the language R. Some minor modifications would allow to translate  
it to Python. The model can later be used in PetroVisor.  

```{r read}
setwd('/home/drome/RProjects/permian/')
hdr = read.csv(file = "header_permian.csv", sep = ",", dec = ".",
               colClasses = c(rep("character", 2), rep("factor", 2),
                              rep("character", 9), "numeric", 
                              rep("character", 3),
                              rep("numeric", 2), "character", rep("numeric", 2)
                              ), na.strings=c("NA","NaN", " ", "NULL")
               )
names(hdr) <- tolower(names(hdr))
hdr <- hdr[hdr$wellstat == 'A',]
hdr <- hdr[hdr$productcd == 'O',]
hdr$wellnm <- paste(hdr$leasenm, paste('-', hdr$wellnr, sep = ''), sep = '')
hdr <- hdr[grep('^(APACHE)', hdr$opernm),]
hdr <- hdr[,c(1,23,2,5,6,7,8,10,11,12,14,15,16,18,19,21,22)]
table(hdr$countynm)
hdr <- hdr[hdr$countynm == 'CRANE',]
table(hdr$formationcd)
hdr <- hdr[hdr$formationcd == '453GBSA',]
hdr[hdr$resrvrnm == 'UNKNOWN' & hdr$formationcd == '453GBSA', 'resrvrnm'] <- 'GRAYBURG/SNAND'
hdr$wellnm <- gsub('--', '-', hdr$wellnm)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
